Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
blargh

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
   ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
   ^2^Department of Biology, Memorial University of Newfoundland, Canada
   #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
    github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
  #bookdown::word_document2:
  #  reference_docx: template.docx
bibliography: ../references/knitcite.bib
#csl: csl.csl
---

@@

## Introduction
Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond_2016] 
to avoid predators [@Bergerud_1985] and access islands during calving
[@Bergerud_1990]. Even for adept swimmers like caribou, the
energetic expenditure of swimming for quadrupedal mammals is
significantly higher than walking or running (Fish 1993), while drowning
is also possible [@Miller_1986]. Despite a large number of coastal and
island caribou herds, only a handful of examples have documented caribou
swimming in the ocean (Table 1).

>>>>

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
   ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
   ^2^Department of Biology, Memorial University of Newfoundland, Canada
   #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
  #  reference_docx: template.docx
bibliography: ../references/knitcite.bib
#csl: csl.csl
---

@@

## Introduction
Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond_2016]
to avoid predators [@Bergerud_1985] and access islands during calving
[@Bergerud_1990]. Even for adept swimmers like caribou, the energetic
expenditure of swimming for quadrupedal mammals is significantly higher than
walking or running, while drowning is also possible [@Miller_1986].
Despite a large number of coastal and island caribou herds, only a handful of
examples have documented caribou swimming in the ocean [e.g. @Jeffery_2007;
@Ricca_2012]. <!-- add Miller 1995/2002 or reference table 1 if we decide to
keep this -->
